Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-28 doc/main_jfm.tex
finished first pass of numerical results

\begin{figure}
\begin{center}
  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  Janus-vesicles in a shear flow. The moving paths of the two centroids
  are plotted in blue and red. The centroids are initially located on
  the $x$-axis. For simulation time, $t = {0, 400,800,1200}$ for
  (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two Janus-vesicles under a shear flow where
  the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). The background color is the
  magnitude of fluid pressure. The color bar is identical for all
  panels. Streamlines are plotted in purple. The insets of all panels
  are generated from simulations of a continuum model of the vesicle and
  the streamlines agree between the two models.}
\end{figure}

@@

\todo[inline]{Bryan left off here}
\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Trajectories of different setups in
  two-vesicle in an extensional flow and the moving paths of two
  centroids of two Janus-vesicles are plotted in blue and red. (i) Both
  centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid
  of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) The
  centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis
  and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid
  of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the
  other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12}
  presents the numerical results from the case (iii) and a consistent
  flow rate is $\chi = 0.005$ for all cases.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two vesicles under an extensional flow where
  the dimensioneless shear rate is $\chi=0.005$; The initial
  configuration is shown in panel (a). The background color indicates
  the magnitude of fluid pressure. From dark red to dark blue, it
  represents the pressure varies from high to low values. The color bar
  is valid for all panels. Streamlines are plotted in purple. The insets
  show the results produced from using continuum model that the
  streamlines have perfect agreements with the present results.}
\end{figure}

@@

With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$. This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
an equilibrium state without separation as shown in case (i). If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward. This is the consequence when the adhesive effect beats the flow strength. In case (iii), two centroids have a small bias in $y$-direction and they
start to move apart along $\pm y$-direction. Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward $\pm y$-directions.

Figure~\ref{figure12} shows numerical results when the centroids of two bodies are placed at
$(-10,-0.1)$ and $(10,0.1)$, that is, case (iii) of Figure~\ref{figure11}. With this setup, 
we can make sure that two Janus-vesicles will separate along $y$-direction eventually and we compare the results against a continuum model as shown in all insets. 
Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.  Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines. In fluid pressure profiles, the pressure is initially high between the gap formed by two 
Janus-vesicles and decreases during the separation. The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  Janus-vesicles suspended in a shear flow. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two Janus-vesicles suspended in a shear flow
  where the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). The background color is the fluid
  pressure. The color bar is identical for all panels. Streamlines are
  plotted in purple. The insets of all panels are generated from
  simulations of a continuum model of the vesicles and the streamlines
  agree between the two models.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Two Janus-vesicles suspended in
  an extensional flow. The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the Janus-vesicles. The flow rate is $\chi = 0.005$ in all cases.
  (i) Both Janus-vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left Janus-vesicle is $0.1$ units above the $x$-axis
  and the right Janus-vesicle is on the $x$-axis. (iii) The centroid of
  the left Janus-vesicle is $0.1$ units above the $x$-axis and the right
  Janus-vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
  the left Janus-vesicle is $0.5$ units above the $x$-axis and the
  centroid of the right Janus-vesicle is $0.5$ units below the $x$-axis.
  Figure~\ref{figure12} presents the numerical results from the case
  (iii).}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two Janus-vesicles suspended in an
  extensional flow where the dimensioneless extensional rate is
  $\chi=0.005$. The centroid of the left Janus-vesicle is $0.1$ units
  above the $x$-axis and the centroid of the right Janus-vesicle is
  $0.1$ units below the $x$-axis. The initial configuration is shown in
  panel (a). The background color is the fluid pressure. The color bar
  is identical for all panels. Streamlines are plotted in purple. The
  insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the models.}
\end{figure}

@@

With a similar setup in the case of two Janus-vesicles in a shear flow,
we use the same two pre-relaxed $58$-body Janus-vesicles and consider
their dynamics in an extensional flow with extensional rate
$\chi=0.005$. This extensional flow is stretching in the $y$ direction
and squeezing in the $x$ direction. Figure~\ref{figure11} shows how the
initial placement of the Janus-vesicles affects the dynamics. When two
centroids are both placed symmetrically on the $x$-axis (case (i)), the
Janus-vesicles reach a steady equilibrium. If one centroid is placed
above the $x$-axis (case (ii)), the two Janus-vesicle move together and
then upward. The migration of the right Janus-vesicle is a consequence
of the adhesive effect created by the hydrophobic interactions. When the
two centroids start on opposite sides of the $x$-axis (case (iii)), they
eventually diverge from one another along the $y$-axis. Finally, when
the two centroids start on opposite sides of the $x$-axis, but with a
greater displacement (case (iv)), the Janus-vesicles move much faster
toward $\pm y$-directions.

Figure~\ref{figure12} shows numerical results when the centroids of two
bodies are placed at $(-10,-0.1)$ and $(10,0.1)$ (case (iii) from
Figure~\ref{figure11}). With this setup, the two
Janus-vesicles eventually separate along $y$-direction and we compare
the results against a continuum model as shown in all insets.  Panels
(b)--(d) show the transient behavior of the Janus-vesicles and continuum
vesicles transitions under an extensional flow. In both the
coarse-grained model and the continuum model, the vesicles initially
converge towards one other and then diverge along the $y$-axis. The
behavior of the streamlines in both cases are similar. The pressure is
initially largest in the gap formed by two Janus-vesicles and decreases
during the separation. The short range repulsion plays an important role
to avoid structure collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.
